### 2016-04-08 misc/notes.tex
updates notes.txt and todo list

In order to perform coherent computations with the singlet-triplet
qubit, we construct an NV / singlet-triplet (ST) SWAP operation:
\begin{align}
  \t{SWAP}^{NV,ST}=\E^{1,2}\t{cNOT}^{1,2}
  \p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
In practice, we cannot couple nuclear spins directly, so we perform
the operation
\begin{align}
  \t{SWAP}^{NV,ST}=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,2}
  \t{SWAP}^{NV,1}\p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Wanting to replace SWAP operations with $i$SWAP operations, we can
equivalently rearrange the above to
\begin{align}
  \t{SWAP}^{NV,ST}=\p{X\t{HG}}^{NV}\t{SWAP}^{NV,1}\E^{NV,2}
  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
\end{align}
and in turn
\begin{multline}
  \t{SWAP}^{NV,ST}\cong \\
  \exp\p{i\f\pi4\sigma_x^{NV}\sigma_x^{ST}}
  \p{X\t{HG}}^{NV}i\t{SWAP}^{NV,1}\E^{NV,2}
  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
  \label{swap_no_zz}
\end{multline}
where
\begin{align}
  \sigma_x^{ST}=\op{S}{T}+\op{T}{S}+iI_r
  \cong\f12\p{\sigma_z^1-\sigma_z^2}.
\end{align}
The construction in (\ref{swap_no_zz}) avoids couplings of the form
$\sigma_z^{NV}\sigma_z^j$.

Alternately, we can construct the SWAP gate from controlled-NOT
operations as
\begin{align}
  \t{SWAP}^{NV,ST}=\t{cNOT}^{NV,ST}\t{cNOT}^{ST,NV}\t{cNOT}^{NV,ST},
\end{align}
where
\begin{align}
  \t{cNOT}^{NV,ST}=\t{c}Z^{NV,1}, &&
  \t{cNOT}^{ST,NV}=\E^{1,2}\t{cNOT}^{1,NV}{\E^\dag}^{1,2}.
\end{align}
We can expand
\begin{align}
  \t{cNOT}^{ST,NV}&=\t{SWAP}^{NV,1}\E^{NV,2}\t{SWAP}^{NV,1}\t{cNOT}^{1,NV}
  \t{SWAP}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1} \\
  &=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Therefore
\begin{align}
  \t{SWAP}^{NV,ST}=\t{c}Z^{NV,1}\t{SWAP}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  \t{SWAP}^{NV,1}\t{c}Z^{NV,1},
\end{align}
which can further be reduced to
\begin{multline}
  \t{SWAP}^{NV,ST}= \\
  R_z^{NV}\p{\f\pi2}R_z^1\p{\f\pi2}{i\t{SWAP}^\dag}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  i\t{SWAP}^{NV,1}R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2}.
  \label{swap_no_zz_cnot}
\end{multline}
The constructions in (\ref{swap_no_zz}) and (\ref{swap_no_zz_cnot})
are theoretically equal (up to global phase), but may have different
fidelities in practice.

@@

\newpage

\section*{Addressing larmor pairs}

When applying a static control field $\v B_{\t{ctl}}$, we have the
effective interaction + control Hamiltonian
\begin{align}
  H=\f12m_s\sigma_z\sum_j\v A_j\c\v I_j-\sum_j\gamma_j\v
  B_{\t{ctl}}\c\v I_j
\end{align}

>>>>

In order to perform coherent computations with the singlet-triplet
qubit, we construct an NV / singlet-triplet (ST) SWAP operation:
\begin{align}
  \t{SWAP}^{NV,ST}=\E^{1,2}\t{cNOT}^{1,2}
  \p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
In practice, we cannot couple nuclear spins directly, so we perform
the operation
\begin{align}
  \t{SWAP}^{NV,ST}=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,2}
  \t{SWAP}^{NV,1}\p{X\t{HG}}^{NV}\t{cNOT}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Wanting to replace SWAP operations with $i$SWAP operations, we can
equivalently rearrange the above to
\begin{align}
  \t{SWAP}^{NV,ST}=\p{X\t{HG}}^{NV}\t{SWAP}^{NV,1}\E^{NV,2}
  \t{cNOT}^{NV,2}{i\t{SWAP}^\dag}^{NV,1}\t{cNOT}^{NV,2}i\t{SWAP}^{NV,1},
  \label{swap_own}
\end{align}

Alternately, we can construct the SWAP gate from controlled-NOT
operations as
\begin{align}
  \t{SWAP}^{NV,ST}=\t{cNOT}^{NV,ST}\t{cNOT}^{ST,NV}\t{cNOT}^{NV,ST},
\end{align}
where
\begin{align}
  \t{cNOT}^{NV,ST}=\t{c}Z^{NV,1}, &&
  \t{cNOT}^{ST,NV}=\E^{1,2}\t{cNOT}^{1,NV}{\E^\dag}^{1,2}.
\end{align}
We can expand
\begin{align}
  \t{cNOT}^{ST,NV}&=\t{SWAP}^{NV,1}\E^{NV,2}\t{SWAP}^{NV,1}\t{cNOT}^{1,NV}
  \t{SWAP}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1} \\
  &=\t{SWAP}^{NV,1}\E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}\t{SWAP}^{NV,1}.
\end{align}
Therefore
\begin{align}
  \t{SWAP}^{NV,ST}=\t{c}Z^{NV,1}\t{SWAP}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  \t{SWAP}^{NV,1}\t{c}Z^{NV,1},
\end{align}
which can further be reduced to
\begin{multline}
  \t{SWAP}^{NV,ST}= \\
  R_z^{NV}\p{\f\pi2}R_z^1\p{\f\pi2}{i\t{SWAP}^\dag}^{NV,1}
  \E^{NV,2}\t{cNOT}^{NV,1}{\E^\dag}^{NV,2}
  i\t{SWAP}^{NV,1}R_z^1\p{-\f\pi2}R_z^{NV}\p{-\f\pi2}.
  \label{swap_cnots}
\end{multline}
The constructions in (\ref{swap_own}) and (\ref{swap_cnots}) are
theoretically equal (up to global phase), but may have different
fidelities in practice.

@@
